### 2025-05-16 manuscript/manuscript.qmd
update data and models
- Subject with age 57 was instead 67.
- Age-adjusted models were refitted
- Figures were re-made to the updated data and models

-   Present the results in a clear, concise, and logical manner.
-   Use tables and figures to effectively visualize the data. Ensure tables and figures are numbered and have descriptive captions.
-   Report relevant statistical results, including p-values, effect sizes, and confidence intervals.
-   Present the main findings first, followed by secondary findings.
-   Avoid repeating data in the text that is already presented in tables or figures, but highlight the most important trends and findings.

>>>>

## Sample Characteristics

[bla bla bla].

## Exercise-Induced Cardiac Autonomic Trajectory

[bla bla bla].

## B Cell Expression on Cardiac Autonomic-Immune Axis

[bla bla bla].

### CD21^+^ / CD11c^-^

[bla bla bla].

### CD21^+^ / CD11c^+^

[bla bla bla].

### CD21^-^ / CD11c^-^

[bla bla bla].

### CD21^-^ / CD11c^+^

[bla bla bla].
